\section{Introduction}

In the dynamic world of web development, choosing the right front-end framework is crucial yet challenging, especially for beginners in the field. With the rapid evolution of the digital landscape, developers, particularly those inexperienced with front-end frameworks, face a challenging decision. In our study, which we conducted without any prior knowledge of front-end frameworks, we hypothesize that a thorough comparative analysis of prominent frameworks like React, Svelte, and Vue can clarify their strengths and weaknesses. This approach aims to aid beginners in making an informed decision about which framework to learn and use.
The decision of selecting a front-end framework is critical. It profoundly influences the development process, application performance, and end-user satisfaction. As the web becomes increasingly integral to our daily lives, ensuring the optimal performance and usability of web applications is not just a technical concern but a necessity for enhancing digital experiences globally.

To address this, our project aims to conduct a comprehensive comparative study of React, Svelte, and Vue. We intend to evaluate these frameworks across crucial parameters like documentation, runtime performance, code quality, and cross-browser compatibility. Our approach involves developing a web application using each framework, adhering to test-driven development principles to ensure consistency and fairness. This methodical evaluation will not only compare these frameworks but also provide insights into their suitability for various development scenarios. 

To expand on this, our project will also place significant emphasis on the subjective experience of the development process. As newcomers to the realm of front-end frameworks, we will document our personal journey with React, Svelte, and Vue. By reflecting on the intuitiveness of the frameworks, the clarity of documentation, and the ease of overcoming challenges, we aim to provide a unique perspective on the learning curve and developer ergonomics of each framework. This personal narrative will complement our objective metrics, offering a comprehensive view of the frameworks from the standpoint of novice developers. This experiential component could be invaluable for beginners who are evaluating these tools for their own use.
