\section{References}

\begin{enumerate}
    \item Acosta, Jan. n.d. “Test-driven development.” IBM. Accessed December 6, 2023. \url{https://www.ibm.com/garage/method/practices/code/practice_test_driven_development/}.
    \item Bhardwaz, Saumyamani, and Rohan Godha. 2023. “Svelte.js: The Most Loved Framework Today.” no. 1, 7.
    \item Copes, Flavio. 2018. “The Vue Handbook: a thorough introduction to Vue.js.” freeCodeCamp. \url{https://www.freecodecamp.org/news/the-vue-handbook-a-thorough-introduction-to-vue-js-1e86835d8446/}.
    \item Faulkner, Rosie. 2023. “Vue vs React vs… Svelte?!.” Medium. \url{https://medium.com/@faulknerproject/vue-vs-react-vs-svelte-5f93d70d2618}.
    \item Ferreira, Fabio, and Marco T. Valente. 2023. “Detecting code smells in React-based Web apps.” no. 1, 16.
    \item HcySun, Yang. 2023. Vue.JS Framework. 1st ed. Singapore: Springer Singapore.
    \item IEEE, Raimundo N. Diniz-Junior, et al. 2022. “Evaluating the performance of web rendering technologies based on JavaScript: Angular, React, and Vue.” \url{https://ieeexplore.ieee.org/document/9959901}.
    \item “Introduction • Docs • SvelteKit.” n.d. SvelteKit. Accessed December 5, 2023. \url{https://kit.svelte.dev/docs/introduction}.
    \item Kaur, Gursheen, and Raj G. Tiwari. 2023. “Comparison and Analysis of Popular Frontend Frameworks and Libraries: An Evaluation of Parameters for Frontend Web Development.” no. 1, 7.
    \item Novac, Cornelia M., et al. 2021. “Comparative study of some applications made in the Vue.js and React.js frameworks.” no. 1, 4.
    \item Perrin, Hunter. n.d. Svelte Material UI. Accessed December 8, 2023. \url{https://sveltematerialui.com/}.
    \item Wichmann, Nick. 2021. “React vs Vue vs Angular vs Svelte.” DEV Community. \url{https://dev.to/hb/react-vs-vue-vs-angular-vs-svelte-1fdm}.
\end{enumerate}
